Unlocking Sensitivity for Visibility-based Estimators of the 21\,cm Reionization Power Spectrum

### 2017-07-24 Rotation paper/draft_working.tex
save

%\documentclass[preprint2,numberedappendix,tighten,twocolappendix]{aastex6}  % USE THIS TO MAKE BIB, THEN FORMAT USING EMULATEAPJ
\documentclass[twocolumn,apj,numberedappendix]{emulateapj}
\shorttitle{Unlocking Sensitivity for 21\,cm Power Spectrum Estimators}
\shortauthors{Zhang, Liu \& Parsons}
\usepackage{float}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[figuresright]{rotating}
%\usepackage{rotating}
\usepackage{natbib}
\usepackage{gensymb}
%\usepackage{pdflscape}
%\usepackage{lscape}
\usepackage{ctable}
\citestyle{aa}
\renewcommand\[{\begin{equation}}
\renewcommand\]{\end{equation}}
\graphicspath{{../figures/}}
\newcommand{\pasa}{PASA}

\begin{document}

@@

\begin{abstract}
Radio interferometers designed to measure the cosmological 21\,cm power spectrum require high sensitivity. Several modern low-frequency interferometers feature drift-scan antennas placed on regular grid to maximize the number of instantaneously coherent (redundant) measurements. However, even for such maximum-redundancy arrays, significant sensitivity comes through partial coherence between baselines. Current visibility-based power spectrum pipelines, though shown to ease control of systematics, lack the ability to make use of this partial redundancy. We introduce a method to leverage partial redundancy in such power spectrum pipelines for drift-scan arrays. Our method cross-multiplies baseline pairs at a time lag and quantifies the sensitivity contributions of each pair of baselines. 
Using the configurations and beams of the 128-element Donald C. Backer Precision Array for Probing the Epoch of Reionization (PAPER-128) and staged deployments of the Hydrogen Epoch of Reionization Array (HERA), we illustrate how our method applies to different arrays and predict the sensitivity improvements associated with pairing partially coherent baselines. As the number of antennas increases, we find partial redundancy to be of increasing importance in unlocking the full sensitivity of upcoming arrays. 
\end{abstract}

@@

We shall use the 128-element PAPER array (henceforth referred to as PAPER-128) to motivate our formalism and demonstrate our method, and extend our results to several HERA configurations in Section \ref{sec:arrconf}. 
The PAPER array is located in the Karoo desert in South Africa (30:43:17.5
S, 21:25:41.8 E). The layout pattern is shown
in Fig. \ref{fig:AntPos}. The array consists of a 112-element core in a rectangular grid, and 16 ``outriggers'' used primarily to aid calibration.  In the bottom panel, the two baselines marked in red are an example of an equivalent pair. We denote a equivalency class of baselines in the PAPER grid by their separations, in this case  \{2,0\}, for the
antennas are separated by 2 units east and 0 units north. Similarly,
the baselines marked in blue and yellow are respectively examples
of \{2,1\} and $\{2, -1\}$.
Note that \{2,0\} and $\{-2, 0\}$ are the same class of baselines and should not be counted twice. Antennas in purely north-south baselines
are close (4m), and hence these baselines are not suitable
for sensitive measurements due to cross-coupling. On the other hand, the small North-South separation means that classes such as \{2,0\} and  \{2,1\} are expected to be near-equivalent. The PAPER-64 analysis of \cite{Ali2015} uses three classes of baselines, the PAPER-128
equivalent of which are 
\{2, 0\}, \{2, 1\} and $\{2, -1\}$. There, baselines are cross-multiplied within each class. This paper provides the method for inter-class multiplications. We will use the short hand notation $\{m,n:m',n'\}$ to denote a pair of baseline classes to be cross-multiplied.

@@

Equivalent baselines follow identical $uvw$ tracks. Traditionally, we can identify
redundancy of nearly equivalent baselines as crossings
of the $uv$ tracks, a two-dimensional projection of $uvw$, as shown in the top panel of Fig. \ref{fig:Tracks}. However, there are several reasons that $uv$ track-crossing does not imply perfect redundancy. The most obvious reason is that the three-dimensional $uvw$ tracks do not actually cross, as is evident from the $vw$ projection in the bottom panel of Fig. \ref{fig:Tracks}. In general, track-crossings are
not accurate enough to determine the optimal time offset for the cross multiplication of visibilities, nor can it provide an estimate of the degree of redundancy.   For drift-scan arrays, even a hypothetical crossing in $uvw$ space would not imply perfect redundancy. This will become evident in the next section, after we develop a more general formalism that accounts for the point spread function of primary. The relation between track-crossing and redundancy for both drift-scan and tracking measurements is further explored in Appendix \ref{sec:appA}.

@@

Ultimately we would like to relate the observed visibility to the power spectrum, $P$, defined such that
\[
\langle \widetilde{T}^{*}(\boldsymbol{k})\widetilde{T}(\boldsymbol{k'})\rangle = \left(2\pi\right)^3\delta_D^3(\bold{k}-\bold{k'})P(k),
\label{eq:Pofk}
\]
where $\bold{k}$ is the cosmological wavenumber, $\delta_D^3$ is the three-dimensional Dirac delta function, and $\widetilde{T}(\boldsymbol{k})$ is the three-dimensional Fourier transform of the brightness temperature field $T(\bold{r})$, with $\bold r$ being the cosmological position coordinate. 
We begin by relating the observational coordinates $\hat{\boldsymbol{s}}$
and $\nu$, to
$\boldsymbol{r}$ and $\boldsymbol{k}$: 
\[
\begin{aligned}r & =\frac{c}{H_{0}}\int_{0}^{z}\frac{dz'}{E(z')}\\
 & \approx\frac{c}{H_{0}}\int_{0}^{z_{0}}\frac{dz'}{E(z')}-\frac{c(1+z_0)^{2}}{\nu_{21}H_{0}E(z_0)}\left(\nu-\nu_{0}\right)\\
 & \equiv X-Y\Delta\nu,
\end{aligned} \label{eq:r}
\]
where $r$ is the magnitude of the vector $\bold{r}$, $\nu_{21}=1.420$\,GHz is the 21\,cm transition rest frequency, $\nu_{0}$ is
a reference central frequency with corresponding redshift $z_{0}$, $H_0$ is the current-day Hubble constant,  
and 
\[
E(z)=\sqrt{\Omega_{m}(1+z)^{3}+\Omega_{\Lambda}}.
\]
Inverting for $\nu$ gives
\begin{equation}
\nu=\frac{X-r}{Y}+\nu_{0}.\label{eq:nur}
\end{equation}
This provides us with a mapping between the observational frequency and the cosmological distance in the radial direction. For the angular directions, we have in the thin-shell limit
\begin{equation}
d^2r=X^2d\Omega. 
\label{eq:thinshell}
\end{equation}
Note that Eq. \eqref{eq:thinshell} does not require the flat-sky approximation; the angular integral is still performed over the curved sky.

@@

\caption{PAPER-128 beam-fringe patterns and their point-spread functions on the $uv$-plane for a frequency of $0.15$\,GHz. Selected baselines have 30-meter East-West separations, and 0- and 4-meter North-South separations, respectively. The top panels show the real parts of the beam-fringe patterns of the baselines (left and middle), and their conjugate product (right). The beam-fringe values are normalized such that the peak of the original beam is unity. 
The bottom-left and middle panels show the peak-normalized $uv$ point spread of the two beam-fringe patterns. The product of the beam spreads displayed in the bottom-right panel shows that power concentrated at $u\approx15$ is recovered. }
\label{fig:beamfringe}
\end{figure*}

@@

At the time offset of maximum redundancy, we expect two baselines to have to same fringe pattern in both frequency and phase. Due to the time offset, however, the beam centers would be slightly shifted with respect to each other. In the top panels of Fig. \ref{fig:beamfringe}, we show the real parts of peak-normalized beam-fringe patterns. The top left and middle panels show the beam-fringe
patterns for the baseline classes \{2,0\} and \{2,1\}, offset by 0.78 hours. More specifically, displayed are the real parts of $g_b\equiv B(\hat{\boldsymbol{s}},\nu)\exp\left[-i2\pi\frac{\nu}{c}\hat{\boldsymbol{s}}\cdot\boldsymbol{b}\right]$ and $g_{b'}\equiv B(\boldsymbol{\Gamma}\hat{\boldsymbol{s}},\nu)\exp\left[-i2\pi\frac{\nu}{c}\boldsymbol{\Gamma}\hat{\boldsymbol{s}}\cdot\boldsymbol{b'}\right]$, respectively. The top right panel show their conjugate product $g_{b}^{*}g_{b'}e^{-i\psi_\nu} = B^{*}(\hat{\boldsymbol{s}},\nu)B(\boldsymbol{\Gamma}\hat{\boldsymbol{s}},\nu)\exp\left[i2\pi\frac{\nu}{c}\left(\hat{\boldsymbol{s}}\cdot\boldsymbol{b}-\boldsymbol{\Gamma}\hat{\boldsymbol{s}}\cdot\boldsymbol{b'}\right)-i\psi_{\nu}\right]$, where we have chosen global phase $\psi_{\nu}$ such that the peak of the conjugate product is real. The product of the beam fringe patterns in the top right shows that the fringes
 cancel out as we expect. Comparing with Eq. \eqref{eq:Thetanu}, we see that $\Theta_\nu=\int d\Omega g_{b}^{*}g_{b'}e^{-i\psi_\nu}$ is the sum over the image shown in the top right panel. At the optimal time offset, the fringe patterns of the two baselines cancel out, leading to a substantial weight $\Theta_\nu$. The frequency-summed weight $\Theta$ is constructed with rephasing as described in Section \ref{sec:rephs} so that the conjugate product (top-right panel) for different frequencies align in phase.

@@

\begin{figure}[h]
\includegraphics[width=\linewidth]{HeraAntpos}
\label{fig:HeraAntpos}
\caption{Planned Hydrogen Epoch of Reionization Array antenna configurations. HERA-37 is expected to complete and start collecting data in August of 2017, and the other three are planned configurations in the next phases. For HERA-350, only the 320 elements in the core are shown. }
\end{figure}

@@

In the middle panel of Fig. \ref{fig:sensplot}
we show $\Theta_{\boldsymbol{bb'}}$ and $\Delta t_{\boldsymbol{bb'}}$ for a variety of baseline combinations. Baseline pairs that are mirror images of each other 
give the same amount of redundancy ($\Theta_{\boldsymbol{bb'}}$), with the opposite time offset, as expected from symmetry. 
For example, \{1,0:1,1\} is mirror image of \{1,0:1,-1\} and these two pairs of baselines
give the same sensibility contribution. Thus we only show a subset of representative baseline pairs to illustrate the contributions. For a more complete result, see Fig. \ref{fig:pairplot}.

As is immediately clear from the figure, baseline pairs that have smaller optimal time offsets
tend to have higher correlations. In other words, correlation peaks
that are closer to zero time offset are higher. This is expected for two reasons;
one is that the longer the time offset of maximum redundancy, the more the sky has moved with respect
to the primary beams and hence the smaller the overlapping patch of sky surveyed. The other reason is that smaller optimal
time offset corresponds to smaller $w$-term-induced decoherence and hence better redundancy.

@@

\item $\Delta t_{\boldsymbol{bb'}}$ vs. $\bar{b}$:
PAPER-128 shows the trend that longer baselines correspond to lower $\Delta t_{\boldsymbol{bb'}}$. HERA arrays do not exhibit this trend here because of a selection effect. Shorter HERA baselines require much longer $\Delta t$ to overlap, partly because of the hexagonal structure requires $60\degree$ of rotation to overlap baselines, partly because of the smaller primary beam. Thus most short HERA baseline pairs are not shown in this figure. Only baseline pairs with $\widetilde{\Theta}_{\boldsymbol{bb'}}>0.01$ are shown.

@@

\item The top sensitivity-contributing near-equivalent pair in each array is normalized to the same $\Theta_{\boldsymbol{bb'}}$ (not shown), but those of HERA arrays have much lower $\widetilde{\Theta}_{\boldsymbol{bb'}}$ than the top pair of PAPER-128. This is because they are longer baselines with lower multiplicity. In the end, these baseline classes still lead to high contributions to total sensitivity (Fig. \ref{fig:osens}) because there are many more such baseline pairs for HERA.

@@

One benefit of delay-transform based power-spectrum estimation is the ability to isolate foregrounds in Fourier space. We show that our proposed estimator does not lead to extra foreground leakage into the EoR window. We then apply our estimator to a variety array configurations. We show that for arrays with increasing number of antennas, partially redundant baselines make up a more significant portion of the array's total sensitivity. The proposed power-spectrum estimator retains benefits of delay-transform techniques for isolating foregrounds and avoiding systematics and enables one to unlock the full sensitivity of a redundant radio interferometer while simultaneously enjoying the benefits of delay-transform techniques for isolating foregrounds and avoiding systematics.

@@

\bibliographystyle{apj}
%\nocite{*}
\bibliography{draft_working}

>>>>

%\documentclass[preprint2,numberedappendix,twocolappendix]{aastex6}  % USE THIS TO MAKE BIB, THEN FORMAT USING EMULATEAPJ
\documentclass[twocolumn,apj,numberedappendix]{emulateapj}
\shorttitle{Unlocking Sensitivity for 21\,cm Power Spectrum Estimators}
\shortauthors{Zhang, Liu \& Parsons}
\usepackage{float}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[figuresright]{rotating}
%\usepackage{rotating}
\usepackage{natbib}
\usepackage{gensymb}
%\usepackage{pdflscape}
%\usepackage{lscape}
\usepackage{ctable}
\citestyle{aa}
\renewcommand\[{\begin{equation}}
\renewcommand\]{\end{equation}}
\graphicspath{{../figures/}}
\newcommand{\pasa}{PASA}
\usepackage[backref,breaklinks,colorlinks,citecolor=blue]{hyperref}
\begin{document}

@@

\begin{abstract}
Radio interferometers designed to measure the cosmological 21\,cm power spectrum require high sensitivity. Several modern low-frequency interferometers feature drift-scan antennas placed on a regular grid to maximize the number of instantaneously coherent (redundant) measurements. However, even for such maximum-redundancy arrays, significant sensitivity comes through partial coherence between baselines. Current visibility-based power spectrum pipelines, though shown to ease control of systematics, lack the ability to make use of this partial redundancy. We introduce a method to leverage partial redundancy in such power spectrum pipelines for drift-scan arrays. Our method cross-multiplies baseline pairs at a time lag and quantifies the sensitivity contributions of each pair of baselines. 
Using the configurations and beams of the 128-element Donald C. Backer Precision Array for Probing the Epoch of Reionization (PAPER-128) and staged deployments of the Hydrogen Epoch of Reionization Array (HERA), we illustrate how our method applies to different arrays and predict the sensitivity improvements associated with pairing partially coherent baselines. As the number of antennas increases, we find partial redundancy to be of increasing importance in unlocking the full sensitivity of upcoming arrays. 
\end{abstract}

@@

We shall use the 128-element PAPER array (henceforth referred to as PAPER-128) to motivate our formalism and demonstrate our method, and extend our results to several HERA configurations in Section \ref{sec:arrconf}. 
The PAPER array is located in the Karoo desert in South Africa (30:43:17.5
S, 21:25:41.8 E). The layout pattern is shown
in Fig. \ref{fig:AntPos}. The array consists of a 112-element core in a rectangular grid, and 16 ``outriggers'' used primarily to aid calibration.  In the bottom panel, the two baselines marked in red are an example of an equivalent pair. We denote a equivalency class of baselines in the PAPER grid by their separations, in this case  \{2,0\}, for the
antennas are separated by 2 units east and 0 units north. Similarly,
the baselines marked in blue and yellow are respectively examples
of \{2,1\} and $\{2, -1\}$.
Note that \{2,0\} and $\{-2, 0\}$ are the same class of baselines and should not be included twice in power-spectrum measurements. Antennas in purely north-south baselines
are close (4m), and hence these baselines are not suitable
for sensitive measurements due to cross-coupling. On the other hand, the small North-South separation means that classes such as \{2,0\} and  \{2,1\} are expected to be near-equivalent. The PAPER-64 analysis of \cite{Ali2015} uses three classes of baselines, the PAPER-128
equivalent of which are 
\{2, 0\}, \{2, 1\} and $\{2, -1\}$. There, baselines are cross-multiplied within each class. This paper provides the method for inter-class multiplications. We will use the short hand notation $\{m,n:m',n'\}$ to denote a pair of baseline classes to be cross-multiplied.

@@

Equivalent baselines follow identical $uvw$ tracks. Traditionally, we can identify
redundancy of nearly equivalent baselines as crossings
of the $uv$ tracks, a two-dimensional projection of $uvw$, as shown in the top panel of Fig. \ref{fig:Tracks}. However, there are several reasons that $uv$ track-crossing does not imply perfect redundancy. The most obvious reason is that the three-dimensional $uvw$ tracks do not actually cross, as is evident from the $vw$ projection in the bottom panel of Fig. \ref{fig:Tracks}. In general, track-crossings are
not accurate enough to determine the optimal time offset for the cross multiplication of visibilities, nor can it provide an estimate of the degree of redundancy.   Furthermore, for drift-scan arrays, even a hypothetical crossing in $uvw$ space would not imply perfect redundancy. This will become evident in the next section, after we develop a more general formalism that accounts for the point spread function of primary. The relation between track-crossing and redundancy for both drift-scan and tracking measurements is further explored in Appendix \ref{sec:appA}.

@@

Ultimately we would like to relate the observed visibility to the power spectrum, $P$, defined such that
\[
\langle \widetilde{T}^{*}(\boldsymbol{k})\widetilde{T}(\boldsymbol{k'})\rangle = \left(2\pi\right)^3\delta_D^3(\bold{k}-\bold{k'})P(k),
\label{eq:Pofk}
\]
where $\bold{k}$ is the cosmological wavenumber, $\delta_D^3$ is the three-dimensional Dirac delta function, and $\widetilde{T}(\boldsymbol{k})$ is the three-dimensional Fourier transform of the brightness temperature field $T(\bold{r})$, with $\bold r$ being the cosmological position coordinate. 
We begin by relating the observational coordinates $\hat{\boldsymbol{s}}$
and $\nu$, to
$\boldsymbol{r}$ and $\boldsymbol{k}$: 
\[
\begin{aligned}r & =\frac{c}{H_{0}}\int_{0}^{z}\frac{dz'}{E(z')}\\
 & \approx\frac{c}{H_{0}}\int_{0}^{z_{0}}\frac{dz'}{E(z')}-\frac{c(1+z_0)^{2}}{\nu_{21}H_{0}E(z_0)}\left(\nu-\nu_{0}\right)\\
 & \equiv X-Y\Delta\nu,
\end{aligned} \label{eq:r}
\]
where $r$ is the magnitude of the vector $\bold{r}$, with $z$ its corresponding redshift. $\nu_{21}=1.420$\,GHz is the 21\,cm transition rest frequency, $\nu_{0}$ is
a reference central frequency with corresponding redshift $z_{0}$, $H_0$ is the current-day Hubble constant,  
and 
\[
E(z)=\sqrt{\Omega_{m}(1+z)^{3}+\Omega_{\Lambda}},
\]
with $\Omega_{m}$ and $\Omega_{\Lambda}$ being respectively the normalized matter and dark energy density.

Inverting Eq. \eqref{eq:r} for $\nu$ gives
\begin{equation}
\nu=\frac{X-r}{Y}+\nu_{0}.\label{eq:nur}
\end{equation}
This provides us with a mapping between the observational frequency and the cosmological distance in the radial direction. For the angular directions, we have in the thin-shell limit
\begin{equation}
d^2r=X^2d\Omega. 
\label{eq:thinshell}
\end{equation}
Note that Eq. \eqref{eq:thinshell} does not require the flat-sky approximation; the angular integral is still performed over the curved sky.

@@

\caption{PAPER-128 beam-fringe patterns and their point-spread functions on the $uv$-plane for a frequency of $0.15$\,GHz. Selected baselines have 30-meter East-West separations. The first baseline, shown in the first column, is purely East-West, while the second baseline, shown in the middle column, has 4-meter North-South separation and has been rotated with a time offset of 0.78 hours. Panels in the top row show the real parts of the beam-fringe patterns of the baselines (left and middle), and their conjugate product (right). The beam-fringe values are normalized such that the peak of the original beam is unity. 
The bottom-left and middle panels show the peak-normalized $uv$ point spread of the two beam-fringe patterns. The product of the beam spreads displayed in the bottom-right panel shows that power concentrated at $u\approx15$ is recovered. }
\label{fig:beamfringe}
\end{figure*}

@@

At the time offset of maximum redundancy, we expect two baselines to have to same fringe pattern in both frequency and phase. Due to the time offset, however, the beam centers would be slightly shifted with respect to each other. In the top panels of Fig. \ref{fig:beamfringe}, we show the real parts of peak-normalized beam-fringe patterns. The top left and middle panels show the beam-fringe
patterns for the baseline classes \{2,0\} and \{2,1\}, offset by 0.78 hours. More specifically, displayed are the real parts of $g_b\equiv B(\hat{\boldsymbol{s}},\nu)\exp\left[-i2\pi\frac{\nu}{c}\hat{\boldsymbol{s}}\cdot\boldsymbol{b}\right]$ and $g_{b'}\equiv B(\boldsymbol{\Gamma}\hat{\boldsymbol{s}},\nu)\exp\left[-i2\pi\frac{\nu}{c}\boldsymbol{\Gamma}\hat{\boldsymbol{s}}\cdot\boldsymbol{b'}\right]$, respectively. The top right panel show their conjugate product $g_{b}^{*}g_{b'}e^{-i\psi_\nu} = B^{*}(\hat{\boldsymbol{s}},\nu)B(\boldsymbol{\Gamma}\hat{\boldsymbol{s}},\nu)\exp\left[i2\pi\frac{\nu}{c}\left(\hat{\boldsymbol{s}}\cdot\boldsymbol{b}-\boldsymbol{\Gamma}\hat{\boldsymbol{s}}\cdot\boldsymbol{b'}\right)-i\psi_{\nu}\right]$, where we have chosen global phase $\psi_{\nu}$ such that the peak of the conjugate product is real. The product of the beam fringe patterns in the top right shows that the fringes
 cancel out as we expect. Comparing with Eq. \eqref{eq:Thetanu}, we see that $\Theta_\nu=\int d\Omega g_{b}^{*}g_{b'}e^{-i\psi_\nu}$ is the sum over the image shown in the top right panel. At the optimal time offset, the fringe patterns of the two baselines cancel out, leading to a substantial weight $\Theta_\nu$. The frequency-summed weight $\Theta$ is constructed with rephasing as described in Section \ref{sec:rephs} so that the conjugate product (top-right panel) for different frequencies align in phase at their peaks. Note it is not possible to align the phase of $g_{b}^{*}g_{b'}e^{-i\psi_\nu}$ for all $(l,m,\nu)$ due to spatial decoherence across the beam as discussed at the end of Section \ref{sec:rephs}.

@@

\begin{figure}[h]
\includegraphics[width=\linewidth]{HeraAntpos}
\label{fig:HeraAntpos}
\caption{Planned Hydrogen Epoch of Reionization Array antenna configurations. HERA-37 is expected to complete and start collecting data in August of 2017, while the other three are planned configurations in the upcoming phases. For HERA-350, only the 320 elements in the core are shown. }
\end{figure}

@@

In the middle panel of Fig. \ref{fig:sensplot}
we show $\Theta_{\boldsymbol{bb'}}$ and $\Delta t_{\boldsymbol{bb'}}$ for a variety of baseline combinations. Baseline pairs that are mirror images of each other 
give approximately the same amount of redundancy ($\Theta_{\boldsymbol{bb'}}$), with the opposite time offset, as expected from symmetry. 
For example, \{1,0:1,1\} is mirror image of \{1,0:1,-1\} and these two pairs of baselines
give the same sensibility contribution. Thus we only show a subset of representative baseline pairs to illustrate the contributions. For a more complete result, see Fig. \ref{fig:pairplot}.

As is immediately clear from the figure, baseline pairs that have smaller optimal time offsets
tend to have higher correlations. In other words, correlation peaks
with closer to zero time offset are higher. This is expected for two reasons;
one is that the longer the time offset of maximum redundancy, the more the sky has moved with respect
to the primary beams and hence the smaller the overlapping patch of sky surveyed. The other reason is that smaller optimal
time offset corresponds to smaller $w$-term-induced decoherence and hence better redundancy.

@@

\item $\Delta t_{\boldsymbol{bb'}}$ vs. $\bar{b}$:
PAPER-128 shows the trend that longer baselines correspond to lower $\Delta t_{\boldsymbol{bb'}}$. HERA arrays do not exhibit this trend here because of a selection effect. Shorter HERA baselines require much longer $\Delta t$ to overlap, partly because of the hexagonal structure requires $60\degree$ of rotation to overlap baselines, partly because of the smaller primary beam. Thus most short HERA baseline pairs are not shown in this figure, as they do not meet the selection criterion $\widetilde{\Theta}_{\boldsymbol{bb'}}>0.01$.

@@

\item The top sensitivity-contributing near-equivalent pair in each array is normalized to have the same $\Theta_{\boldsymbol{bb'}}$ (not shown), but those of HERA arrays have much lower $\widetilde{\Theta}_{\boldsymbol{bb'}}$ than the top pair of PAPER-128. This is because they are longer baselines with lower multiplicity. In the end, these baseline classes still lead to high contributions to total sensitivity (Fig. \ref{fig:osens}) because there are many more such baseline pairs for HERA.

@@

One benefit of delay-transform based power-spectrum estimation is the ability to isolate foregrounds in Fourier space. We show that our proposed estimator does not lead to extra foreground leakage into the EoR window. We then apply our estimator to a variety array configurations. We show that for arrays with increasing number of antennas, partially redundant baselines make up a more significant portion of the array's total sensitivity. The proposed power-spectrum estimator enables one to unlock the full sensitivity of a redundant radio interferometer while retaining the benefits of delay-transform techniques for isolating foregrounds and avoiding systematics.

@@

\bibliographystyle{apj}
%\nocite{*}
\bibliography{draft_final}
